Case Study: scRNA-seq (Mouse data, scDD method)

### 2018-03-27 datasets/GWAS/GWAS.Rmd
Remove covariate heatmaps and boxplots

# upset plot 
plotFDRMethodsOverlap(sbN, 
                      alpha=0.05, nsets=ncol(sb),
                      order.by="freq", decreasing=TRUE,
                      supplementary=FALSE)

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf",
             "scott-empirical", "scott-theoretical")
mcols(sbN)$ind_covariate <- mcols(sbN)$ind_covar_N
plotCovariateBoxplots(sbN, alpha=0.1, nsets=6, methods=methods, trans=log2, maxNum=3) +
    ggtitle("Covariate 1: Sample size")
```

```{r, fig.width=8, fig.height=3.5}
mcols(sbN)$tstat <- bmi %>% filter(!is.na(ind_covar_N)) %>% pull(effect_size)
covariateHeatmap(sbN, alpha=0.05, covname="tstat", trans = "log1p")
covariateHeatmap(sbN, alpha=0.05, covname="ind_covar_N", trans = "log1p")

covariateHeatmap(sbN, alpha=0.05, covname="tstat", nbins=25, 
                 linePlot = TRUE, trans="log1p")
covariateHeatmap(sbN, alpha=0.05, covname="ind_covar_N", nbins=25, 
                 linePlot = TRUE, trans="log1p")
```

@@

# upset plot 
plotFDRMethodsOverlap(sbAF, 
                      alpha=0.05, nsets=ncol(sbAF),
                      order.by="freq", decreasing=TRUE,
                      supplementary=FALSE)

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf",
             "scott-empirical", "scott-theoretical")
mcols(sbAF)$ind_covariate <- abs(mcols(sbAF)$ind_covar_AF-0.5)
plotCovariateBoxplots(sbAF, alpha=0.1, nsets=6, methods=methods, maxNum=3)+
  ggtitle("Covariate 2: Minor allele frequency")
```

```{r, fig.width=8, fig.height=3.5}
mcols(sbAF)$tstat <- bmi %>% filter(!is.na(ind_covar_AF)) %>% pull(effect_size)
covariateHeatmap(sbAF, alpha=0.05, covname="tstat", trans = "log1p")
covariateHeatmap(sbAF, alpha=0.05, covname="ind_covar_AF")

covariateHeatmap(sbAF, alpha=0.05, covname="tstat", nbins=25, 
                 linePlot = TRUE, trans = "log1p")
covariateHeatmap(sbAF, alpha=0.05, covname="ind_covar_AF", nbins=25, 
                 linePlot = TRUE)
```

>>>>

# upset plot 
plotFDRMethodsOverlap(sbN, 
                      alpha=0.05, nsets=ncol(sb),
                      order.by="freq", decreasing=TRUE,
                      supplementary=FALSE) 
```

```{r, fig.width=8, fig.height=3.5}
mcols(sbN)$ind_covariate <- mcols(sbN)$ind_covar_N
mcols(sbN)$tstat <- bmi %>% filter(!is.na(ind_covar_N)) %>% pull(effect_size)
covariateHeatmap(sbN, alpha=0.05, covname="tstat", nbins=25, 
                 linePlot = TRUE, trans="log1p")
covariateHeatmap(sbN, alpha=0.05, covname="ind_covar_N", nbins=25, 
                 linePlot = TRUE, trans="log1p")
```

@@

# upset plot 
plotFDRMethodsOverlap(sbAF, 
                      alpha=0.05, nsets=ncol(sbAF),
                      order.by="freq", decreasing=TRUE,
                      supplementary=FALSE)
```

```{r, fig.width=8, fig.height=3.5}
mcols(sbAF)$ind_covariate <- abs(mcols(sbAF)$ind_covar_AF-0.5)
mcols(sbAF)$tstat <- bmi %>% filter(!is.na(ind_covar_AF)) %>% pull(effect_size)
covariateHeatmap(sbAF, alpha=0.05, covname="tstat", nbins=25, 
                 linePlot = TRUE, trans = "log1p")
covariateHeatmap(sbAF, alpha=0.05, covname="ind_covar_AF", nbins=25, 
                 linePlot = TRUE)
```

### 2018-03-27 datasets/scrnaseq/scrnaseq-human-mast.Rmd
Remove covariate heatmaps and boxplots

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf",
             "scott-empirical", "scott-theoretical")
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
plotCovariateBoxplots(sb1, alpha=0.1, nsets=6, methods=methods, trans=log2, maxNum=3) +
  ggtitle("MAST, Covariate 1: Mean Nonzero Expression")

@@

```{r, fig.width=8, fig.height=3.5}
covariateHeatmap(sb1, alpha=0.05, covname="ind_covariate") +
  ggtitle("MAST, Covariate 1: Mean Nonzero Expression")

covariateHeatmap(sb1, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE) +
  ggtitle("MAST, Covariate 1: Mean Nonzero Expression")
```

@@

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf",
             "scott-empirical", "scott-theoretical")
mcols(sb2)$ind_covariate <- mcols(sb2)$detection
plotCovariateBoxplots(sb2, alpha=0.1, nsets=6, methods=methods, maxNum=3)+
  ggtitle("MAST, Covariate 2: Detection Rate")

@@

```{r, fig.width=8, fig.height=3.5}
covariateHeatmap(sb2, alpha=0.05, covname="ind_covariate") +
  ggtitle("MAST, Covariate 2: Detection Rate")

covariateHeatmap(sb2, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE) +
  ggtitle("MAST, Covariate 2: Detection Rate")
```

>>>>

@@

```{r, fig.width=8, fig.height=3.5}
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
covariateHeatmap(sb1, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE) +
  ggtitle("MAST, Covariate 1: Mean Nonzero Expression")
```

@@

@@

```{r, fig.width=8, fig.height=3.5}
mcols(sb2)$ind_covariate <- mcols(sb2)$detection
covariateHeatmap(sb2, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE) +
  ggtitle("MAST, Covariate 2: Detection Rate")
```

### 2018-03-27 datasets/scrnaseq/scrnaseq-human-scdd.Rmd
Remove covariate heatmaps and boxplots

# upset plot 
plotFDRMethodsOverlap(sb1, 
                      alpha=0.05, nsets=ncol(sb1),
                      order.by="freq", decreasing=TRUE,
                      supplementary=FALSE)

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf",
             "scott-empirical", "scott-theoretical")
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
plotCovariateBoxplots(sb1, alpha=0.1, nsets=6, methods=methods, trans=log2, maxNum=3) +
  ggtitle("scDD, Covariate 1: Mean Nonzero Expression")

```

```{r, fig.width=8, fig.height=3.5}
covariateHeatmap(sb1, alpha=0.05, covname="ind_covariate") +
  ggtitle("scDD, Covariate 1: Mean Nonzero Expression")

covariateHeatmap(sb1, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE) +
  ggtitle("scDD, Covariate 1: Mean Nonzero Expression")
```

@@

# upset plot 
plotFDRMethodsOverlap(sb2, 
                      alpha=0.05, nsets=ncol(sb2),
                      order.by="freq", decreasing=TRUE,
                      supplementary=FALSE)

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf",
             "scott-empirical", "scott-theoretical")
mcols(sb2)$ind_covariate <- mcols(sb2)$detection
plotCovariateBoxplots(sb2, alpha=0.1, nsets=6, methods=methods, maxNum=3) +
  ggtitle("scDD, Covariate 2: Detection Rate")

```

```{r, fig.width=8, fig.height=3.5}
covariateHeatmap(sb2, alpha=0.05, covname="ind_covariate") +
  ggtitle("scDD, Covariate 2: Detection Rate")

covariateHeatmap(sb2, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE) +
  ggtitle("scDD, Covariate 2: Detection Rate")
```

>>>>

# upset plot 
plotFDRMethodsOverlap(sb1, 
                      alpha=0.05, nsets=ncol(sb1),
                      order.by="freq", decreasing=TRUE,
                      supplementary=FALSE) 
```

```{r, fig.width=8, fig.height=3.5}
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
covariateHeatmap(sb1, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE) +
  ggtitle("scDD, Covariate 1: Mean Nonzero Expression")
```

@@

# upset plot 
plotFDRMethodsOverlap(sb2, 
                      alpha=0.05, nsets=ncol(sb2),
                      order.by="freq", decreasing=TRUE,
                      supplementary=FALSE)
```

```{r, fig.width=8, fig.height=3.5}
mcols(sb2)$ind_covariate <- mcols(sb2)$detection
covariateHeatmap(sb2, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE) +
  ggtitle("scDD, Covariate 2: Detection Rate")
```

### 2018-03-27 datasets/scrnaseq/scrnaseq-mouse-mast.Rmd
Remove covariate heatmaps and boxplots

# upset plot 
plotFDRMethodsOverlap(sb1, 
                      alpha=0.05, nsets=ncol(sb1),
                      order.by="freq", decreasing=TRUE,
                      supplementary=FALSE)

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf",
             "scott-empirical", "scott-theoretical")
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
plotCovariateBoxplots(sb1, alpha=0.1, nsets=6, methods=methods, trans=log2, maxNum=3) +
  ggtitle("MAST, Covariate 1: Mean Nonzero Expression")

```

```{r, fig.width=8, fig.height=3.5}
covariateHeatmap(sb1, alpha=0.05, covname="ind_covariate") +
  ggtitle("MAST, Covariate 1: Mean Nonzero Expression")

covariateHeatmap(sb1, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE, trans = "log1p") +
  ggtitle("MAST, Covariate 1: Mean Nonzero Expression")
```

@@

# upset plot 
plotFDRMethodsOverlap(sb2, 
                      alpha=0.05, nsets=ncol(sb2),
                      order.by="freq", decreasing=TRUE,
                      supplementary=FALSE)

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf",
             "scott-empirical", "scott-theoretical")
mcols(sb2)$ind_covariate <- mcols(sb2)$detection
plotCovariateBoxplots(sb2, alpha=0.1, nsets=6, methods=methods, maxNum=3) +
  ggtitle("MAST, Covariate 2: Detection Rate")

```

```{r, fig.width=8, fig.height=3.5}
covariateHeatmap(sb2, alpha=0.05, covname="ind_covariate") +
  ggtitle("MAST, Covariate 2: Detection Rate")

covariateHeatmap(sb2, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE) +
  ggtitle("MAST, Covariate 2: Detection Rate")
```

>>>>

# upset plot 
plotFDRMethodsOverlap(sb1, 
                      alpha=0.05, nsets=ncol(sb1),
                      order.by="freq", decreasing=TRUE,
                      supplementary=FALSE) 
```

```{r, fig.width=8, fig.height=3.5}
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
covariateHeatmap(sb1, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE, trans = "log1p") +
  ggtitle("MAST, Covariate 1: Mean Nonzero Expression")
```

@@

# upset plot 
plotFDRMethodsOverlap(sb2, 
                      alpha=0.05, nsets=ncol(sb2),
                      order.by="freq", decreasing=TRUE,
                      supplementary=FALSE)
```

```{r, fig.width=8, fig.height=3.5}
mcols(sb2)$ind_covariate <- mcols(sb2)$detection
covariateHeatmap(sb2, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE) +
  ggtitle("MAST, Covariate 2: Detection Rate")
```

### 2018-03-27 datasets/scrnaseq/scrnaseq-mouse-scdd.Rmd
Remove covariate heatmaps and boxplots

# upset plot 
plotFDRMethodsOverlap(sb1, 
                      alpha=0.05, nsets=ncol(sb1),
                      order.by="freq", decreasing=TRUE,
                      supplementary=FALSE)

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf",
             "scott-empirical", "scott-theoretical")
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
plotCovariateBoxplots(sb1, alpha=0.1, nsets=6, methods=methods, trans=log2, maxNum=3) +
  ggtitle("scDD, Covariate 1: Mean Nonzero Expression")

```

```{r, fig.width=8, fig.height=3.5}
covariateHeatmap(sb1, alpha=0.05, covname="ind_covariate") +
  ggtitle("scDD, Covariate 1: Mean Nonzero Expression")

covariateHeatmap(sb1, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE, trans = "log1p") +
  ggtitle("scDD, Covariate 1: Mean Nonzero Expression")
```

>>>>

# upset plot 
plotFDRMethodsOverlap(sb1, 
                      alpha=0.05, nsets=ncol(sb1),
                      order.by="freq", decreasing=TRUE,
                      supplementary=FALSE) 
```

```{r, fig.width=8, fig.height=3.5}
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
covariateHeatmap(sb1, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE, trans = "log1p") +
  ggtitle("scDD, Covariate 1: Mean Nonzero Expression")
```
